Hydras \& Co.

### 2022-11-28 doc/chapter-fol.tex
Example of folLogic

>>>>

\section{Derived rules and natural deduction}

 The library 
 \href{../theories/html/hydras.Ackermann.folLogic.html}{Ackermann.folLogic} contains many derived rules which allow the user to build proofs in a natural deduction style (with introduction and elimination rules).

\subsection{Example}

For instance, let us prove Peirce's rule.
 (in  ~\href{../theories/html/hydras.MoreAck.folPeirce.html}{MoreAck.folPeirce} ).

\subsubsection{Prelude}

\inputsnippets{folPeirce/prelude}

\subsection{Proof of Pierce's law}

\inputsnippets{folPeirce/PeirceProof}

Let us try to do an implication introduction.

\inputsnippets{folPeirce/step1}

Now, we may use the law of excluded middle with the formula $P$. The only non-trivial case is about $\sim P$.

\inputsnippets{folPeirce/step2}

The rest of the proof is composed of basic proof steps, 
and bookkeeping steps (about \texttt{Ensembles.In}).

\inputsnippets{folPeirce/step3, folPeirce/step4}
